---
title: "Untitled"
author: '123'
date: "2021/2/18"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
data("chickwts")
data1=subset(chickwts,feed=="meatmeal")
data1
data2=subset(chickwts,feed=="sunflower")
data2
```
a
the two samples t-test: (not paired)
Because the lengths of the two types are different, the paired test cannot be used
Null hypothesis: the distribution between meatmeal and sunflower is the same
Alternative hypothesis: the distribution between meatmeal and sunflower is not the same

```{r}
t.test(data1$weight,data2$weight)
```

It can be seen that the p value of t-test is less than 0.05, so the null hypothesis can be rejected, that is, the distribution between meatmeal and sunflower is not the same.

the Mann-Whitney test
Null hypothesis: the distribution between meatmeal and sunflower is the same
Alternative hypothesis: the distribution between meatmeal and sunflower is not the same
```{r}
wilcox.test(data1$weight,data2$weight)
```

It can be seen that Mann-Whitney
The p value of test is greater than 0.05, so the null hypothesis is considered acceptable, that is, the distribution between meatmeal and sunflower is the same.

the Kolmogorov-Smirnov test:
Null hypothesis: the distribution between meatmeal and sunflower is the same
Alternative hypothesis: the distribution between meatmeal and sunflower is not the same
```{r}
ks.test(data1$weight,data2$weight)
```

It can be seen that the p value of the Kolmogorov-Smirnov test is greater than 0.05, so the null hypothesis is considered acceptable, that is, the distribution between meatmeal and sunflower is the same.

Parametric tests reject the null hypothesis, and non-parametric tests accept the null hypothesis.

b
one-way ANOVA:

```{r}
library(gplots)
plotmeans(weight~feed,data=chickwts)
```

According to the above results, the larger the mean, the better the effect, so sunflower has the best effect

c
relevant diagnostic tools:
Null hypothesis: The weights of these 6 feeds are significantly the same
Alternative hypothesis: the weights of these 6 feeds are significantly different

```{r}
nlevels(chickwts$feed)
fit=aov(weight~feed,data=chickwts)
summary(fit)
```

It can be seen that the p value of one-way ANOVA is less than 0.05, so it is considered that the null hypothesis is rejected, that is, the weights of the 6 feeds are considered to be significantly different.

d
Kruskal-Wallis test:
Null hypothesis: the weights distribution between different feeds is the same
Alternative hypothesis: the distribution of weights between different feeds is not the same
```{r}
kruskal.test(weight~feed,data=chickwts)
```

It can be seen that the p value of the Kruskal-Wallis test is less than 0.05, so it is considered that the null hypothesis is rejected, that is, the weights of the 6 feeds are considered to be significantly different.
The result is the same, the main differences between them are:
Kruskal-Wallis one-way analysis of variance is mainly used when comparing between multiple groups, because the groups do not meet the normal distribution and cannot be compared by ANOVA, the statistical similarity test method often used.
